Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-13 paper/sheaf_lics.tex
good sheafification

We have to be careful~: if we want to propagate the properties of the
first modality $\modal_{-1}$, all the higher modalities $\modal_n$ must be compatible
with $\modal_{-1}$, \ie we want the property
\begin{prop}
  If $P:\HProp$, and $\widehat P$ is $P$ seen as a $\Type_n$, then $\modal_n \widehat P = \modal_{-1} P$, and the
  following coherence diagram commute 
  $$\xymatrix{
    \modal_{-1} P \ar@{=}[r] & \modal_n \widehat P \\
    P \ar@{=}[r] \ar[u]^{\eta_{-1}} & \widehat P \ar[u]_{\eta_n}
  }$$
\end{prop}

@@

\subsection{From Type to Separated Type}
\label{ssec:from-type-separated}
In this section, we suppose given a truncation index $n\geqslant -1$,
and a left exact modality $\modal$ on $\Type_n$, compatible with the
modality on $\HProp$.

@@

The last thing to prove is the cumulativity of our sheafifications~:
\begin{prop}
  If $T:\Type_n$, then $\modal T = \star \widehat T$ (where $\widehat
  T$ is $T$ seen as a $\Type_{n+1}$.
\end{prop}
\section{Future Works}
\label{sec:future-works}

>>>>

We have to be careful~: if we want to propagate the properties of the
first modality $\modal_{-1}$, all the higher modalities $\modal_n$ must be compatible
with $\modal_{-1}$, \ie we want the property
\begin{prop}\label{prop:hprop}
  If $P:\HProp$, and $\widehat P$ is $P$ seen as a $\Type_n$, then $\modal_n \widehat P = \modal_{-1} P$, and the
  following coherence diagram commute 
  $$\xymatrix{
    \modal_{-1} P \ar@{=}[r] & \modal_n \widehat P \\
    P \ar@{=}[r] \ar[u]^{\eta_{-1}} & \widehat P \ar[u]_{\eta_n}
  }$$
\end{prop}

@@

\subsection{From Type to Separated Type}
\label{ssec:from-type-separated}
In this section, we suppose given a truncation index $n\geqslant -1$,
and a left exact modality $\modal$ on $\Type_n$, compatible with the
modality on $\HProp$ in the sense of proposition~\ref{prop:hprop}.

@@

The last thing to prove is the cumulativity of our sheafifications~:
\begin{prop}
  If $T:\Type_n$, then $\modal T = \star \widehat T$ (where $\widehat
  T$ is $T$ seen as a $\Type_{n+1}$.
\end{prop}
It will imply that $\star$ is compatible with $\HProp$ in the sense of proposition~\ref{prop:hprop}.
\section{Future Works}
\label{sec:future-works}
